---
title: "Looking Ahead to Heating Prices at the Start of the Next Two Heating Seasons in Maine"
author: "Roux Institute - Analytics Capstone Spring 2022"
output: html_document
---
```{r echo=FALSE}
knitr::opts_chunk$set(fig.width=8, fig.height=4, fig.align="center") 
# Comments about see user guide for instructions
```
<br>

```{r SETUP, include=FALSE}

# Packages required for this markdown file
list.of.packages <- c("readxl", "dplyr", "lubridate", "forecast", "tidyr",
                      "ggplot2", "kableExtra")

# Check which packages from the list have not been installed on local machine,
# and install those which have not.
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

# Load packages
library(readxl)
library(dplyr)
library(lubridate)
library(forecast)
library(tidyr)
library(ggplot2)
library(kableExtra)

# Set working directory to folder containing this .Rmd file
setwd(dirname(rstudioapi::getSourceEditorContext()$path))

# Supress warning messages
warn = getOption("warn")
options(warn=-1)

```

```{r DEFINE FUNCTIONS, include=FALSE}

# FUNCTION TO INSERT MISSING MONTHS INTO MONTYLY DATA WITH NA PRICE
missing_months <- function(df) {
  
  # Find the column named "month" in the dataframe
  month_column <- df[ , which(colnames(df)=="month")]
  
  # Create new dataframe with full range of months from first to last month
  first_month <- min(month_column)
  last_month <- max(month_column)
  month_range <- data.frame(seq(first_month, last_month, by="month"))
  colnames(month_range) <- "month"
  
  # Merge month_range with original df
  df <- merge(month_range, df, by="month", all.x = TRUE)
  
  return(df)
}
```



```{r IMPORT HEATING OIL DATA, include=FALSE}

# Define file name/location and import
file <- file.path("data", "historical propane - k1 - #2 price tables_charts1.xlsx")
heatingoil <- as.data.frame(
  read_excel(file, sheet = "#2 chart & monthly averages",
             range = cell_cols("A:B"),
             col_names = c("month", "heatingoil_per_gal"),
             col_types = c("date", "numeric")
  ))
heatingoil <- heatingoil[-c(1,2), ]  # remove 1st two rows (contain NA only)

# Convert month to Date format
heatingoil$month <- as.Date(heatingoil$month)

# Fill in missing months
heatingoil <- missing_months(heatingoil)

# Find earliest month in heating oil price data to use as basis for other datasets
startmonth <- as.Date(min(heatingoil$month)) 
endmonth <- as.Date(max(heatingoil$month)) 

```


```{r IMPORT DIESEL DATA, include=FALSE}
# NOTE: This data is used to impute the missing values of heating oil prices

# Define file name/location and import
file <- file.path("data", "psw18vwall.xls")
diesel <- as.data.frame(
  read_excel(file, 
             sheet = "Data 2",
             range = cell_cols("A:D"),
             col_names = c("month", "delete", "delete2", "diesel_per_gal"),
             col_types = c("date", "numeric", "numeric", "numeric")
  ))
diesel <- diesel[-c(1,3), ]  # remove 1st three rows (contain NA only)

# Delete middle two columns (data for other regions)
diesel <- dplyr::select(diesel, c(-delete, -delete2))

# Dates for diesel prices are currently for the 15th of the month
# Revise to be the 1st of the month to match other datasets
diesel$month <- as.Date(floor_date(as.Date(diesel$month), unit="months"))

# Remove dates with no pricing data (NA) at the beginning 
diesel <- diesel[!is.na(diesel$diesel_per_gal),]

# Filter diesel data to start/end at the same point as heating oil data
diesel <- diesel %>% 
  filter(month >= startmonth) %>% 
  filter(month <= endmonth)

```


```{r IMPUTE MISSING HEATING OIL PRICES, include=FALSE}

# Merge diesel prices with heating oil prices
heatingoil <- merge(heatingoil, diesel, by="month")
heatingoil$original <- heatingoil$heatingoil_per_gal

# Define linear regession model for relationship between heating oil and diesel prices
linear_mod <- lm(heatingoil_per_gal ~ diesel_per_gal, data=heatingoil)

# Calculate imputed heating oil price value using linear model
heatingoil$imputed_per_gal <- linear_mod$coefficients[1] + 
  (heatingoil$diesel_per_gal * linear_mod$coefficients[2])

# Replace NA's with imputed values 
heatingoil$heatingoil_per_gal <- ifelse(is.na(heatingoil$heatingoil_per_gal),
       heatingoil$imputed_per_gal, heatingoil$heatingoil_per_gal)

# Reduce dataframe to only contain month and heating oil price (incl imputed vals)
heatingoil <- dplyr::select(heatingoil, c(month, heatingoil_per_gal))

```


```{r IMPORT ELECTRICITY DATA, include=FALSE}

# Define file name/location and import
file <- file.path("data", "sales_revenue.xlsx")
electricity <- as.data.frame(
  read_excel(file,
             sheet = "Monthly-States",
             range = cell_cols("A:H"),
             col_names = c("year", "month", "state", "data_status","revenue",
                           "sales", "customers", "electricity_per_kwh"),
             col_types = c("numeric", "numeric", "text", "text", "numeric",
                           "numeric", "numeric", "numeric")
             )
  )
electricity <- electricity[-c(1:3), ]  # remove 1st three rows
electricity <- electricity %>%
  filter(state == "ME") %>%            # keep only Maine data
  dplyr::select(-c(data_status, customers))   # remove unnecessary columns

# Convert cents per kwh to dollars per kwh
electricity$electricity_per_kwh <- electricity$electricity_per_kwh/100

# Remove all columns except year, month, and price
electricity <- electricity %>% dplyr::select(c(year, month, electricity_per_kwh))

# Combine year and month and dummy "01" day into date
electricity$combined_date = as.Date(paste0(electricity$year,"-",
                                           electricity$month,"-01"), tz="UTC")

# To match format of heating oil data, rename columns and drop unnecessary ones
electricity <- electricity[ , c("combined_date", "electricity_per_kwh")]
colnames(electricity) <- c("month", "electricity_per_kwh")

# Sort from least recent to most recent
electricity <- electricity %>% arrange(month)

```


```{r HEATING OIL PRICE FORECAST, include=FALSE}
# Start date for forecast
begin <- as.Date("2005-01-01")

# Define objects for first month and year in the data
startyear <- year(begin)
startmon <- month(begin)

# Filter for begin
filtered <- heatingoil %>%
  filter(month >= begin)

# Define time series object w/ heating oil price data
ho_ts <- ts(filtered$heatingoil_per_gal, frequency = 12,
            start=c(startyear, startmon))

# Make 30-month forecast for each model
heatingoil30 <- forecast(arima(ho_ts, c(2,0,0)), 30)

# Create sequence of dates for the 30 predicted months
start_pred_o <- filtered$month[length(filtered$month)] %m+% months(1)
end_pred_o <- filtered$month[length(filtered$month)] %m+% months(30)

# Create dataframe for storing predicted values
pred <- data.frame(
  month = seq(start_pred_o, end_pred_o, "months"),
  fore = heatingoil30$mean
)

# Get full range of months, historic and predicted
all_months <- data.frame(
  month = c(filtered$month, pred$month))

# Combine historic and predicted data
heatingoil_forecast <- left_join(all_months, filtered, by="month")
heatingoil_forecast <- left_join(heatingoil_forecast, pred, by="month")

# Make column for combined historic and predicted data
heatingoil_forecast$dollars_per_gal <- rowSums(heatingoil_forecast[ 
  ,c("heatingoil_per_gal", "fore")]
  , na.rm=TRUE)

# Change column names
colnames(heatingoil_forecast) <- c("month",
                                   "heatoil_historic_dollars_per_gal",
                                   "heatoil_predicted_dollars_per_gal",
                                   "heatoil_dollars_per_gal")

```


```{r ELECTRICITY PRICE FORECAST, include=FALSE}

# Filter for begin
filtered <- electricity %>%
  filter(month >= begin)

# Define time series object w/ heating oil price data
el_ts <- ts(filtered$electricity_per_kwh, frequency = 12,
            start=c(startyear, startmon))

# Make 30-month forecast
electricity30 <- rwf(el_ts, drift=TRUE, 30)

# Create sequence of dates for the 30 predicted months
start_pred_e <- filtered$month[length(filtered$month)] %m+% months(1)
end_pred_e <- filtered$month[length(filtered$month)] %m+% months(30)

# Create dataframe for storing predicted values
pred <- data.frame(
  month = seq(start_pred_e, end_pred_e, "months"),
  fore = electricity30$mean
)

# Get full range of months, historic and predicted
all_months <- data.frame(
  month = c(filtered$month, pred$month))

# Combine historic and predicted data
electricity_forecast <- left_join(all_months, filtered, by="month")
electricity_forecast <- left_join(electricity_forecast, pred, by="month")

# Make column for combined historic and predicted data
electricity_forecast$dollars_per_kwh <- rowSums(electricity_forecast[ 
  ,c("electricity_per_kwh", "fore")]
  , na.rm=TRUE)

# Change column names
colnames(electricity_forecast) <- c("month",
                                   "elect_historic_dollars_per_kwh",
                                   "elect_predicted_dollars_per_kwh",
                                   "elect_dollars_per_kwh")

```


```{r MERGE INTO SINGLE DATAFRAME, include=FALSE}
df <- merge(heatingoil_forecast, electricity_forecast, by="month")

```


```{r CALCULATE PER BTU, include=FALSE}

# Define Efficiencies =  c(BTU's per unit, System Efficiency, Distribution Efficiency)
electric_heat_pump <- c(3412, 2.93, 1.00)
oil_boiler <- c(139000, 0.87, 0.80)
electric_baseboard <- c(3412, 1.00, 1.00)

## Calculate $ per million BTU historic, predicted, and combined for each heating type
# Oil Boiler
df$oilboiler_historic_dollars_per_milBTU <- 
  1000000 * df$heatoil_historic_dollars_per_gal /
  (oil_boiler[1]*oil_boiler[2]*oil_boiler[3])
df$oilboiler_predicted_dollars_per_milBTU <- 
  1000000 * df$heatoil_predicted_dollars_per_gal /
  (oil_boiler[1]*oil_boiler[2]*oil_boiler[3])
df$oilboiler_dollars_per_milBTU <- 
  1000000 * df$heatoil_dollars_per_gal /
  (oil_boiler[1]*oil_boiler[2]*oil_boiler[3])
# Electric Baseboard
df$electbaseb_historic_dollars_per_milBTU <- 
  1000000 * df$elect_historic_dollars_per_kwh /
  (electric_baseboard[1]*electric_baseboard[2]*electric_baseboard[3])
df$electbaseb_predicted_dollars_per_milBTU <- 
  1000000 * df$elect_predicted_dollars_per_kwh /
  (electric_baseboard[1]*electric_baseboard[2]*electric_baseboard[3])
df$electbaseb_dollars_per_milBTU <- 
  1000000 * df$elect_dollars_per_kwh /
  (electric_baseboard[1]*electric_baseboard[2]*electric_baseboard[3])
# Electric Heat Pump
df$electheatp_historic_dollars_per_milBTU <- 
  1000000 * df$elect_historic_dollars_per_kwh /
  (electric_heat_pump[1]*electric_heat_pump[2]*electric_heat_pump[3])
df$electheatp_predicted_dollars_per_milBTU <- 
  1000000 * df$elect_predicted_dollars_per_kwh /
  (electric_heat_pump[1]*electric_heat_pump[2]*electric_heat_pump[3])
df$electheatp_dollars_per_milBTU <- 
  1000000 * df$elect_dollars_per_kwh /
  (electric_heat_pump[1]*electric_heat_pump[2]*electric_heat_pump[3])
```


```{r CALCULATE PER TYPICAL HOUSE, include=FALSE}
# Assume 80 million BTU per year
# Oil Boiler
df$oilboiler_historic_dollars_per_80milBTU<- 
  df$oilboiler_historic_dollars_per_milBTU * 80
df$oilboiler_predicted_dollars_per_80milBTU <- 
  df$oilboiler_predicted_dollars_per_milBTU * 80
df$oilboiler_dollars_per_80milBTU <- 
  df$oilboiler_dollars_per_milBTU * 80
# Electric Baseboard
df$electbaseb_historic_dollars_per_80milBTU <- 
  df$electbaseb_historic_dollars_per_milBTU * 80
df$electbaseb_predicted_dollars_per_80milBTU <- 
  df$electbaseb_predicted_dollars_per_milBTU * 80
df$electbaseb_dollars_per_80milBTU <- 
  df$electbaseb_dollars_per_milBTU * 80
# Electric Heat Pump
df$electheatp_historic_dollars_per_80milBTU <- 
  df$electheatp_historic_dollars_per_milBTU * 80
df$electheatp_predicted_dollars_per_80milBTU <- 
  df$electheatp_predicted_dollars_per_milBTU * 80
df$electheatp_dollars_per_80milBTU <- 
  df$electheatp_dollars_per_milBTU * 80

```

---

```{r PLOT HEATING OIL FORECAST, echo=FALSE}
# Select columns for use in plot
plot_df <- select(df, c(
  month,
  heatoil_historic_dollars_per_gal, 
  heatoil_predicted_dollars_per_gal
  ))

# Rename columns
colnames(plot_df) <- c("month", "historic", "predicted")

# Pivot long to make format better for ggplot
plot_df <- plot_df %>% 
  pivot_longer(!month, names_to="time", values_to="dollars_per_gal")

# Define some variables to be used in plotting:
Labels = c("Historic Price", "Predicted Price")
upperlimit_o <- ceiling(max(df$heatoil_dollars_per_gal))

# Plot
ggplot(data=plot_df,
       aes(x=month, y=dollars_per_gal, size=time, col=time, linetype=time)) +
  geom_line() +
  scale_size_manual(values = c(1, 1), labels = Labels) +
  scale_linetype_manual(values = c(1,2), labels = Labels) +
  scale_color_manual(values=c("black",  "blue"), labels = Labels) +
  scale_x_date(limits=c((start_pred_o %m-% months(121)), end_pred_o),
               date_breaks="6 months", date_labels="%b%Y", expand = c(0, 0)) +
  scale_y_continuous(labels=scales::dollar_format(accuracy=0.01),
                     limits=c(0,upperlimit_o)) +
  labs(title="30-Month Heating Oil Price Forecast for Maine ($/gal)*") +
       #y=""
  guides(col=guide_legend(""),
         size=guide_legend(""),
         linetype=guide_legend("")) +
  theme(legend.key.size =  unit(0.5, "in"),
        panel.background = element_blank(),
        panel.grid.major = element_line(color="gray85", linetype = "dotted"),
        plot.title = element_text(size=18, hjust=0.5, face="bold"),
        axis.title.x = element_blank(),
        axis.text.x = element_text(size=10, angle=45, hjust=1),
        axis.text.y = element_text(size=12, face="bold"),
        axis.title.y = element_blank(),
        axis.ticks = element_blank(),
        legend.position = "top",
        legend.text = element_text(size=12),
        legend.key = element_rect(fill = NA, color = NA))



```

```{r HEATING OIL COST TABLE, echo=FALSE}

thisOct <- as.Date(paste0(year(now()),"-10-01"))
nextOct <- thisOct %m+% years(1)

colsnames <- c(format(thisOct, "%b %Y"), format(nextOct, "%b %Y"))
thisOctprice <- paste("$", unlist(sprintf("%.2f",
  df[df$month == thisOct, c("heatoil_predicted_dollars_per_gal")])))
nextOctprice <- paste("$", unlist(sprintf("%.2f",
  df[df$month == nextOct, c("heatoil_predicted_dollars_per_gal")])))
prices <- c(thisOctprice, nextOctprice)

df_table <- data.frame(colsnames, prices)
colnames(df_table) <- c(" ", "Est. Price per Gallon*")


df_table %>%
  kbl(align="c") %>%
  kable_styling("striped", full_width=FALSE, font_size=16, position="center")  %>%
  column_spec(1, bold=TRUE) %>%
  column_spec(2, bold=TRUE, color="blue") 
```

---

<br>
```{r PLOT ELECTRICITY FORECAST, echo=FALSE}
# Select columns for use in plot
plot_df <- select(df, c(
  month,
  elect_historic_dollars_per_kwh, 
  elect_predicted_dollars_per_kwh
  ))

# Rename columns
colnames(plot_df) <- c("month", "historic", "predicted")

# Pivot long to make format better for ggplot
plot_df <- plot_df %>% 
  pivot_longer(!month, names_to="time", values_to="dollars_per_kwh")

# Define some variables to be used in plotting:
Labels = c("Historic Price", "Predicted Price")
upperlimit_e <- ceiling(max(df$elect_dollars_per_kwh)*2) / 2


# Plot
ggplot(data=plot_df,
       aes(x=month, y=dollars_per_kwh, size=time, col=time, linetype=time)) +
  geom_line() +
  scale_size_manual(values = c(1, 1), labels = Labels) +
  scale_linetype_manual(values = c(1,2), labels = Labels) +
  scale_color_manual(values=c("black",  "red"), labels = Labels) +
  scale_x_date(limits=c((start_pred_e %m-% months(121)), end_pred_e),
               date_breaks="6 months", date_labels="%b%Y", expand = c(0, 0)) +
  scale_y_continuous(labels=scales::dollar_format(accuracy=0.01),
                     limits=c(0,upperlimit_e)) +
  labs(title="30-Month Electricity Price Forecast for Maine ($/kwh)*") +
       #y=""
  guides(col=guide_legend(""),
         size=guide_legend(""),
         linetype=guide_legend("")) +
  theme(legend.key.size =  unit(0.5, "in"),
        panel.background = element_blank(),
        panel.grid.major = element_line(color="gray85", linetype = "dotted"),
        plot.title = element_text(size=18, hjust=0.5, face="bold"),
        axis.title.x = element_blank(),
        axis.text.x = element_text(size=10, angle=45, hjust=1),
        axis.text.y = element_text(size=12, face="bold"),
        axis.title.y = element_blank(),
        axis.ticks = element_blank(),
        legend.position = "top",
        legend.text = element_text(size=12),
        legend.key = element_rect(fill = NA, color = NA))



```

```{r ELECTRICITY COST TABLE, echo=FALSE}

thisOctprice <- paste("$", unlist(sprintf("%.3f",
  df[df$month == thisOct, c("elect_predicted_dollars_per_kwh")])))
nextOctprice <- paste("$", unlist(sprintf("%.3f",
  df[df$month == nextOct, c("elect_predicted_dollars_per_kwh")])))
prices <- c(thisOctprice, nextOctprice)

df_table <- data.frame(colsnames, prices)
colnames(df_table) <- c(" ", "Est. Price per kWh*")


df_table %>%
  kbl(align="c") %>%
  kable_styling("striped", full_width=FALSE, font_size=16, position="center")  %>%
  column_spec(1, bold=TRUE) %>%
  column_spec(2, bold=TRUE, color="red") 
```

---

<br>
```{r PLOT DOLLARS PER MILLION BTU COMPARISON, echo=FALSE}
# Select columns for use in plot
plot_df <- select(df, c(
  month,
  oilboiler_historic_dollars_per_milBTU, 
  oilboiler_predicted_dollars_per_milBTU,
  electbaseb_historic_dollars_per_milBTU, 
  electbaseb_predicted_dollars_per_milBTU,
  electheatp_historic_dollars_per_milBTU, 
  electheatp_predicted_dollars_per_milBTU
  ))

# Rename columns
colnames(plot_df) <- c("month", "ob_historic", "ob_predicted", 
                       "ebb_historic", "ebb_predicted",
                       "ehp_historic", "ehp_predicted")

# Pivot long to make format better for ggplot
plot_df <- plot_df %>% 
  pivot_longer(!month, names_to="heat", values_to="dollars_per_milBTU")

# Provide order
plot_df$heat <- factor(
  plot_df$heat, 
  levels=c("ob_historic", "ob_predicted", 
                       "ebb_historic", "ebb_predicted",
                       "ehp_historic", "ehp_predicted"))

# Define some variables to be used in plotting:
Labels = c("Oil Boiler (Historic)", "Oil Boiler (Predicted)",
           "Electric Baseboard (Historic)", "Electric Baseboard (Predicted)",
           "Electric Heat Pump (Historic)", "Electric Heat Pump (Predicted)")
Labels = c(" ", "Oil Boiler",
           " ", "Electric Baseboard",
           " ", "Electric Heat Pump")


upperlimit_btu <- ceiling(max(pmax(
  df$oilboiler_historic_dollars_per_milBTU,
  df$oilboiler_predicted_dollars_per_milBTU,
  df$electbaseb_historic_dollars_per_milBTU,
  df$electbaseb_predicted_dollars_per_milBTU,
  df$electheatp_historic_dollars_per_milBTU,
  df$electheatp_predicted_dollars_per_milBTU, na.rm=TRUE))/10)*10

# Plot
ggplot(data=plot_df,
       aes(x=month, y=dollars_per_milBTU, size=heat, 
           col=heat, 
           linetype=heat)) +
  geom_line() +
  scale_size_manual(values = c(1, 1, 1, 1, 1, 1), labels = Labels) +
  scale_linetype_manual(values = c(1,2,1,2,1,2), labels = Labels) +
  scale_color_manual(values=c("blue",  "blue",
                              "orange", "orange",
                              "red", "red"), labels = Labels) +
  scale_x_date(limits=c((start_pred_o %m-% months(121)), end_pred_o),
               date_breaks="6 months", 
               date_labels="%b%Y", 
               expand = expansion(mult = c(0, 0.25))) +
  scale_y_continuous(labels=scales::dollar_format(accuracy=0.01),
                    limits=c(0,upperlimit_btu)) +
  labs(title="Heating Price Forecast Comparison ($ per million BTU)*") +
  geom_text(aes(label="Oil Boiler"), 
            x=end_pred_o, y=last(df$oilboiler_predicted_dollars_per_milBTU), 
            size=4, col="blue", hjust = -0.01, vjust=0.5) +
  geom_text(aes(label="Electric Baseboard"), 
            x=end_pred_e, y=last(df$electbaseb_predicted_dollars_per_milBTU), 
            size=4, col="orange", hjust = -0.01, vjust=0.5) +
  geom_text(aes(label="Electric Heat Pump"), 
            x=end_pred_e, y=last(df$electheatp_predicted_dollars_per_milBTU), 
            size=4, col="red", hjust = -0.01, vjust=0.5) +
  theme(legend.key.size =  unit(0.5, "in"),
        panel.background = element_blank(),
        panel.grid.major = element_line(color="gray85", linetype = "dotted"),
        plot.title = element_text(size=18, hjust=0.5, face="bold"),
        axis.title.x = element_blank(),
        axis.text.x = element_text(size=10, angle=45, hjust=1 #, color=datecolor
                                   ),
        axis.text.y = element_text(size=12, face="bold"),
        axis.title.y = element_blank(),
        axis.ticks = element_blank(),
        legend.position = "none"
        #legend.position = "top",
        #legend.text = element_text(size=10),
        #legend.key = element_rect(fill = NA, color = NA)
        )



```


```{r COMPARE COST PER MILLION BTU TABLE, echo=FALSE}

col1 <- c("Electric Baseboard", "Oil Boiler", "Electric Heat Pump")
col2 <- unlist(df[df$month == thisOct, c("electbaseb_dollars_per_milBTU", "oilboiler_dollars_per_milBTU", "electheatp_dollars_per_milBTU")])
col3 <- unlist(df[df$month == nextOct, c("electbaseb_dollars_per_milBTU", "oilboiler_dollars_per_milBTU", "electheatp_dollars_per_milBTU")])

df_table <- as.data.frame(cbind(col2, col3))

mult_oilfurn_thisOct <- round(df_table[2,1] / df_table[3,1],1)
mult_oilfurn_nextOct <- round(df_table[2,2] / df_table[3,2],1)
mult_electbaseb_thisOct <- round(df_table[1,1] / df_table[3,1],1)
mult_electbaseb_nextOct <- round(df_table[1,2] / df_table[3,2],1)

df_table$col2 <- paste("$",round(df_table$col2, 2))
df_table$col3 <- paste("$",round(df_table$col3, 2))
rownames(df_table) <- col1
colnames(df_table) <- c(
  format(as.Date(thisOct), "%b %Y"),
  format(as.Date(nextOct), "%b %Y")
                        )

df_table %>% 
  kbl() %>%
  kable_styling("striped", full_width=FALSE, font_size=18) %>%
  row_spec(1, bold=TRUE, color="orange") %>%
  row_spec(2, bold=TRUE, color="blue") %>%
  row_spec(3, bold=TRUE, color="red")


```
<br>
<br>
In<font size="4"> **`r toString(format(as.Date(thisOct), "%b %Y"))`**, </font>heating with an <font size="4"><span style="color: blue;">**oil boiler**</span></font> is estimated to cost<font size="4"> **`r mult_oilfurn_thisOct` x** </font>more than heating with <font size="4"><span style="color: red;">**electric heat pumps**</span></font>,<br>
and heating with <font size="4"><span style="color: orange;">**electric baseboard heating**</span></font> is estimated to cost<font size="4"> **`r mult_electbaseb_thisOct` x** </font>more than heating with <font size="4"><span style="color: red;">**electric heat pumps**</span></font>.

<br>

In<font size="4"> **`r toString(format(as.Date(nextOct), "%b %Y"))`**, </font>heating with an <font size="4"><span style="color: blue;">**oil boiler**</span></font> is estimated to cost<font size="4"> **`r mult_oilfurn_nextOct` x** </font>more than heating with <font size="4"><span style="color: red;">**electric heat pumps**</span></font>,<br>
and heating with <font size="4"><span style="color: orange;">**electric baseboard heating**</span></font> is estimated to cost<font size="4"> **`r mult_electbaseb_nextOct` x** </font>more than heating with <font size="4"><span style="color: red;">**electric heat pumps**</span></font>.
<br>
<br>

---

***\*Notes:***

* *Historic heating oil prices obtained from the State of Maine Governor's Energy Office data.*
* *Historic heating oil prices for non-heating-season months that were missing from the data were obtained by imputation using a linear regression model based on U.S. On-Highway Diesel Fuel Prices obtained from the U.S. Energy Information Administration.*
* *Heating oil prices predicted using an ARIMA(2,0,0) model, which has a 1-month forecast Mean Absolute Percentage Error (MAPE) of 3.44%, a 6-month forecast MAPE of 12.83%, and an 18-month forecast MAPE of 22.69%.*
* *Historic electricity prices obtained from the U.S. Energy Information Administration's average monthly residential price, which is calculated by total revenue divided by the number of customers.*
* *Electricity prices predicted using a random walk with drift model, which has a 1-month forecast Mean Absolute Percentage Error (MAPE) of 1.51%, a 6-month forecast MAPE of 3.30%, and an 18-month forecast MAPE of 4.95%.*
* *Calculating dollars per million BTU for each heating type was performed using BTU's per unit, system efficiencies, and distribution efficiencies obtained from Efficiency Maine.*
<br>
<br>
<br>

---

